DRAFT: Towards a paper on patient movement in the Victorian hospital system

### 2025-03-27 reports/sketch.qmd
attempt path normalisation

```{python}
#| echo: false
import netsim_summariser as summ
import polars as pl
import seaborn as sns
import numpy as np
from matplotlib import pyplot as plt
from scipy import stats

sns.set()
sns.set_palette('colorblind')
```

```{python}
metrics_archives = {
    'temporal': './zero_sims/temporal/metrics_30s.parquet',
    'static': './zero_sims/static/metrics_30s_fa.parquet',
    'snapshot': './zero_sims/snapshot/metrics_30s_fa.parquet',
    'naive_static': './zero_sims/naive_static/metrics_30s.parquet',
}

@@

analytical_expected_hitting_naive = pl.read_csv("./hitting_time_analysis/numer_hitting_time_30indv_chains.csv")
ana_E_hitT_naive = np.sort(analytical_expected_hitting_naive.select('hitting_time').to_series().to_numpy().flatten())

>>>>

```{python}
#| echo: false
import netsim_summariser as summ
import polars as pl
import seaborn as sns
import numpy as np
from matplotlib import pyplot as plt
from scipy import stats
from pathlib import Path

sns.set()
sns.set_palette('colorblind')
sns.set_context('paper')

root = Path("../")
```

```{python}
metrics_archives = {
    'temporal': root / 'simulations/zero_sims/temporal/metrics_30s.parquet',
    'static': root / 'simulations/zero_sims/static/metrics_30s_fa.parquet',
    'snapshot': root / 'simulations/zero_sims/snapshot/metrics_30s_fa.parquet',
    'naive_static': root / 'simulations/zero_sims/naive_static/metrics_30s.parquet',
}

@@

analytical_expected_hitting_naive = pl.read_csv(root / "outputs/hitting_time_analysis/numer_hitting_time_30indv_chains.csv")
ana_E_hitT_naive = np.sort(analytical_expected_hitting_naive.select('hitting_time').to_series().to_numpy().flatten())
